### 2008-08-22 doc/a-rex/arex_tech_doc.tex
Fixing a-rex document to represent bes/internal/reported staates consistently.

\begin{itemize}
\item ACCEPTED/\textbf{Accepted}
\item PREPARING/\textbf{Preparing}
\item SUBMITTING/\textbf{Submiting}
\item INLRMS/\textbf{Executing}
\item FINISHING/\textbf{Finishing}
\item FINISHED/\textbf{Finished}
\item CANCELING/\textbf{Killing}
\item DELETED/\textbf{Deleted}
\end{itemize}
\end{itemize}
See section \ref{Section: Job Flow} for a description of the various
states. Additionally each value can be prepended the prefix {}``PENDING:''
(like PENDING:ACCEPTED, see section \ref{Section: Job Flow}). This
is used to show that a job is \emph{ready} to be moved to the next
state but it has to stay in it's current state \emph{only} because
otherwise some limits set in the configuration would be exceeded.

@@

\begin{tabular}{|c|c|>{\raggedright}p{10cm}|}
\hline 
Applicable BES State&
ARC Sub-state&
\multicolumn{1}{c|}{Description}\tabularnewline
\hline
\hline 
\renewcommand{\multirowsetup}{\centering}\multirow{2}{2cm}{Pending}&
Accepting&
Job is in the process of being submitted\tabularnewline
\cline{2-2} \cline{3-3} 
\multicolumn{1}{|c|}{}&
Accepted&
Job was submitted\tabularnewline
\hline 
\renewcommand{\multirowsetup}{\centering}\multirow{7}{2cm}{Running}&
Preparing&
Stage-in process is going on\tabularnewline
\cline{2-2} \cline{3-3} 
\multicolumn{1}{|c|}{}&
Prepared&
Stage-in process has finished\tabularnewline
\cline{2-2} \cline{3-3} 
\multicolumn{1}{|c|}{}&
Submiting&
Communication with local batch system is in process\tabularnewline
\cline{2-2} \cline{3-3} 
\multicolumn{1}{|c|}{}&
Executing&
Job is being executed in local batch system\tabularnewline
\cline{2-2} \cline{3-3} 
\multicolumn{1}{|c|}{}&
Killing&
Communication with local batch system to terminate execution is in
process\tabularnewline
\cline{2-2} \cline{3-3} 
\multicolumn{1}{|c|}{}&
Executed&
Job execution in local batch system has finished\tabularnewline
\cline{2-2} \cline{3-3} 
\multicolumn{1}{|c|}{}&
Finishing&
Stage-out process is going on\tabularnewline
\hline 
Cancelled&
Finished&
There was a failure during execution\tabularnewline
\cline{1-1} 
Failed&
\multicolumn{1}{c|}{}&
\multicolumn{1}{l|}{}\tabularnewline
\hline 
Finished&
Finished&
Job finished successfully\tabularnewline
\hline 
Finished&
Deleted&
Job finished and was left in A-REX too long\tabularnewline
\hline 
All&
Pending&
Job is prevented from going to the next state due to some internal
limits; this sub-state appears in parallel with other sub-states\tabularnewline
\hline 
All&
Held&
Job processing is suspended on client request; this sub-state appears
in parallel with other sub-states. This state is reserved for future
and i snot implemented yet.\tabularnewline
\hline
\end{tabular}
\end{table}

>>>>

\begin{itemize}
\item ACCEPTED
\item PREPARING
\item SUBMIT
\item INLRMS
\item FINISHING
\item FINISHED
\item CANCELING
\item DELETED
\end{itemize}
\end{itemize}
See section \ref{Section: Job Flow} for a description of the various
states. Additionally each value can be prepended the prefix {}``PENDING:''
(like PENDING:ACCEPTED, see section \ref{Section: Job Flow}). This
is used to show that a job is \emph{ready} to be moved to the next
state but it has to stay in it's current state \emph{only} because
otherwise some limits set in the configuration would be exceeded.

@@

\begin{tabular}{|c|c|c|>{\raggedright}p{10cm}|}
\hline 
Applicable BES State&
ARC Sub-state&
A-REX internal state&
\multicolumn{1}{c|}{Description}\tabularnewline
\hline
\hline 
\renewcommand{\multirowsetup}{\centering}\multirow{2}{2cm}{Pending}&
Accepting&
ACCEPTED&
Job is in the process of being submitted. This state is not recognised
by the A-REX yet. \emph{Accepted} is first reported state.\tabularnewline
\cline{2-2} \cline{3-3} \cline{4-4} 
\multicolumn{1}{|c|}{}&
Accepted&
ACCEPTED&
Job was submitted\tabularnewline
\hline 
\renewcommand{\multirowsetup}{\centering}\multirow{7}{2cm}{Running}&
Preparing&
PREPARING&
Stage-in process is going on\tabularnewline
\cline{2-2} \cline{3-3} \cline{4-4} 
\multicolumn{1}{|c|}{}&
Prepared&
PREPARING+PENDING&
Stage-in process has finished\tabularnewline
\cline{2-2} \cline{3-3} \cline{4-4} 
\multicolumn{1}{|c|}{}&
Submiting&
SUBMIT&
Communication with local batch system is in process\tabularnewline
\cline{2-2} \cline{3-3} \cline{4-4} 
&
\multicolumn{1}{c|}{Queued}&
\multicolumn{1}{c|}{INLRMS}&
\multicolumn{1}{p{10cm}|}{Job entered local batch system but is not runnning now. This state
is not recognised by the A-REX yet. \emph{Executing} is reported instead }\tabularnewline
\cline{2-2} \cline{3-3} \cline{4-4} 
\multicolumn{1}{|c|}{}&
Executing&
INLRMS&
Job is being executed in local batch system\tabularnewline
\cline{2-2} \cline{3-3} \cline{4-4} 
\multicolumn{1}{|c|}{}&
Executed&
INLRMS,INLRMS+PENDING&
Job execution in local batch system has finished. The A-REX dos not
detect job states inside local batch system yet. As result this state
is reported only if job is \emph{Pending}.\tabularnewline
\cline{2-2} \cline{3-3} \cline{4-4} 
\multicolumn{1}{|c|}{}&
Killing&
CANCELING&
Communication with local batch system to terminate execution is in
process\tabularnewline
\cline{2-2} \cline{3-3} \cline{4-4} 
\multicolumn{1}{|c|}{}&
Finishing&
FINISHING&
Stage-out process is going on\tabularnewline
\hline 
Cancelled&
Killed&
FINISHED&
Job was stopped by explicit user request. The A-REX currently does
not remember this request. \emph{Failed} is reported instead.\tabularnewline
\hline 
\multicolumn{1}{|c|}{Failed}&
\multicolumn{1}{c|}{Failed}&
FINISHED&
\multicolumn{1}{l|}{There was a failure during execution}\tabularnewline
\hline 
Finished&
Finished&
FINISHED&
Job finished successfully\tabularnewline
\hline 
Finished&
Deleted&
DELETED&
Job finished and was left in A-REX too long\tabularnewline
\hline 
All&
Pending&
PENDING&
Job is prevented from going to the next state due to some internal
limits; this sub-state appears in parallel with other sub-states\tabularnewline
\hline 
All&
Held&
&
Job processing is suspended on client request; this sub-state appears
in parallel with other sub-states. This state is reserved for future
and is not implemented yet.\tabularnewline
\hline
\end{tabular}
\end{table}
